The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching

### 2017-03-27 article.tex
Add section on version identifiers.

>>>>

\subsubsection*{Stability and Version Identifier}

Prior to CDK \cdkversion{}, the parity of the version identifier's second digit 
indicated stability. Even numbers (v1.2.x, v1.4.x) indicating API stability and
odd numbers (v1.3.x, v1.5.x) indicating potential API instability. Versions 
v1.4.x and v1.5.x were developed in parallel, where possible patches were
applied to both. As the APIs diverged the amount of effort to port patches
from the development but more robust v1.5.x to v1.4.x 
became unmanageable for the core development team. This even-odd version scheme
was adopted from old Linux kernal versioning that was subsequently
abandoned in 2004 for time-based releases~\cite{LinuxKernalVersionNumbering}.

At the time of writing the development branch is more than 3000 commits ahead
of v1.4.x. As the the v1.5.x API has become stable it became time to release 
v1.6.x. Due to significant API changes in 2011\footnote{https://github.com/cdk/cdk/commit/2fc6b61972af834c1fea7fcb64287363ecbcb188}
it was felt a larger digit increment was needed. This provided the 
opportunity to change to a more manageable and intuitive version identifier.

From CDK \cdkversion{} a new sequence based version scheme will be used. The
version identifier indicates change significance as follows:

\begin{verbatim}
{MAJOR}.{MINOR}.{PATCH}

MAJOR: API change/removed
MINOR: New feature (API added)
PATCH: Bug fix
\end{verbatim}

Due to limited developer resources we envision that releases will primarily 
increment the minor version with the occasional patch release. As per Maven 
convention, development versions are suffixed with \texttt{-SNAPSHOT}. 
There are no API changes from v1.5.x and v2.0.
